%!TEX root = ../proteoform_suite_manual.tex
%---------------------------------------------------------------------
%	PROJECT OVERVIEW
%---------------------------------------------------------------------

% Project overview -- detachable. Note: work on the titling here: I want the title to be on the same page as the project overview, so it can be detached.

%[state big picture]
%[state motivation]
%[state problem definition]
\pagebreak
\addcontentsline{toc}{section}{Overview}
\section*{Project Overview}

Proteoform Suite is a user interface for the analysis of proteoform MS data. The source-code is openly available at \url{https://github.com/smith-chem-wisc/proteoform-suite}. This software identifies and quantifies proteoforms by comparing the intact mass for each observed proteoform to theoretical proteoforms generated from known protein sequences and annotated post-translational modifications (PTMs) as well as to other coeluting observed proteoforms. These comparisons reveal both exact-mass matches and mass differences characteristic of known PTMs. Proteoforms are grouped together based on these mass differences into proteoform families. A proteoform family is the set of proteoforms derived from a given gene. Bottom-up peptide identifications and top-down proteoform identifications can be integrated into the analysis to improve proteoform identifications. The program also quantifies relative proteoform abundances between two conditions by calculating intensity ratios for each identified proteoform. Finally, Proteoform Suite streamlines the visualization of proteoform families as networks in the program Cytoscape. 
\\
\subsection*{Key Publications}
\begin{itemize}
\item \fullcite{Shortreed2016}
\item \fullcite{Cesnik2018}
\item \fullcite{Dai2017}
\item  \fullcite{Schaffer2018b}
\item \fullcite{Schaffer2018}
\item \fullcite{Dai2019}
\item \fullcite{Schaffer2019a}
\item \fullcite{Schaffer2020}
\end{itemize}