%!TEX root = ../proteoform_suite_manual.tex
%---------------------------------------------------------------------
%	THEORETICAL DATABASE
%---------------------------------------------------------------------

\section{Theoretical Database}

\subsection{Theoretical Proteoforms}
overview of what's going on here (generating expected theoretical proteoforms from xmls and ptmlists)
\begin{itemize}
	\item data table column overview
	\item Types to exclude (MT tag in ptmlist)
	\item Max number of PTMs to include
	\item minimum length?
	\item Combining sequence-identical proteins (why)
	\item Combining mass-identical proteoforms (why)	
	\item Option to limit combinatorial expansion (limit triples) and why do that
\end{itemize}

\subsection{Decoy Databases}
decoy databases and why they're important; 
\begin{itemize}
	\item how we're generating them
	\item specifying number of decoy databases. When would you want more? 
	\item Max number of PTMs to include
	\item Option to limit combinatorial expansion (limit triples) and why do that
\end{itemize}

\subsection{Fixed and Variable Modifications}
\begin{itemize}
	\item Variable oxidation
	\item Fixed carbamidomethylation
	\item cleaved N-met (fixed)
\end{itemize}

\subsection{Isotope Composition}
\begin{itemize}
	\item Natural (unlabeled)
	\item NeuCode Light (used for 2:1, light:heavy)
	\item NeuCode Heavy (used for 2:1, heavy:light? untested. note likely implications if used for analysis.)
\end{itemize}

\subsection{Modification Options}
Proteoforms are identified considering the likelihood that a mass difference is represented by a PTM set. The frequency of each mod is used to assess this. The display names and the likelihood of each mod can be customized. 
\begin{itemize}
	\item Types to exclude (MT tag in ptmlist), why you'd want to do that (e.g. mods that are for tryptic peptides)
	\item Customizing modification names for cytoscape output and otherwise
	\item Saving custom mod names, amending stored mod names (probably more of the latter)
	\item How mod rank heuristics are computed, why you'd want to change them
	\item Notes on column headers
\end{itemize}

\subsection{Eliminating Modification in PTM list from identifications}
\begin{itemize}
	\item Set mod rank high (necessary?)
	\item Set mod proteoform requirement to yes (reject PTM sets with that mass)
	\item Unaccept peaks for mass differences near that singular mass (reject singular PTM)
\end{itemize}
